\section{Homework 0}
\begin{enumerate}
    \item (a) CS70 Website (click): \url{www.eecs70.org} \\
          (b) HW: 10\%, Midterm 1: 25\%, Midterm 2: 25\%, Final: 40\%
    \item (a) \boxed{\text{Yes.}} Alice and Bob cannot write up a solution together. They must each write up their solutions independently. \\
          (b) \boxed{\text{No.}} Taking notes is fine, as long as Carol isn't directly copying what Dan is saying. She did indeed write up her solution by herself, and credited Dan for his ideas. \\
          (c) \boxed{\text{No.}} Using the same approach from a website source is fine as long as Erin didn't copy any parts verbatim and she cites the website, which she did. \\
          (d) \boxed{\text{Yes.}} This is not fine as Frank copied Grace's written solution verbatim. Therefore, he was technically in possession of another student's solution, which makes him a naughty child. \\
          (e) \boxed{\text{Yes.}} This is not fine as Irene was in possession of another student's (Heidi's) solution.
    \item (a) The post number for the Note 0 thread is \href{https://piazza.com/class/jkjku77a1h451b?cid=13}{13} \\
          (b) Comment: "Could you be more specific? Which parts of the proof do you get (in your own words), and which parts are you having trouble with? You could also try going to office hours or a homework party."
    \item (a) $\forall x \exists y((P(x)\wedge Q(x, y)) \implies x \leq \sqrt{y})$ \\
          (b) $\sum\limits_{i=0}^k i = \frac{k(k+1)}{2}$
\end{enumerate}